### 2022-05-27 main/chapter_2ljets.tex
clarify mt2

Tagging adds labels to objects.
For jets in $\twoljets$, $b$-tagging is used to identify jets which are
more likely to have originated from $b$ quarks;
these tags serve to improve our separation of $t\bar t$ backgrounds and
of signals producing $Z/h \rightarrow b\bar b$ decays.

@@

@@

To be precise, the stransverse mass explores how to split the observed
$\ptmiss$ between the two visible decay products in an event, and can be
defined as
\begin{equation}
\mttwo(a_\mu, b_\mu, m)
=
\min_{\vec p\,+\,\vec q\,=\,\ptmiss}
\max
\begin{Bmatrix}
m_T(a_\mu + \{\!\sqrt{m^2 - \vec p_T^{\:2}},\,\vec p\,\}_\mu)\\
m_T(b_\mu + \{\!\sqrt{m^2 - \vec q_T^{\:2}},\,\vec q\,\}_\mu)\\
\end{Bmatrix}
,
\end{equation}
in which $m_T^2(p_\mu) = p_0^2 - p_1^2 - p_2^2$~\cite{lester1999measuring}.
As an extension, one can assign different masses $m_p$ and $m_q$ to the
the two invisible products~\cite{lester2015bisection}.

Numerical evaluation of $\mttwo$ can be performed efficiently with interval
bisection algorithms, which seek the least resonance mass for which the
transverse masses allow any compatible missing momentum
assignment~\cite{cheng2008minimal, lester2015bisection}.
Public code for calculating $\mttwo$ is available as a Python
library~\cite{gillam2021mt2}, to which I contributed a faster and more robust
implementation of the bisection algorithm by
Lester and Nachman~\cite{lester2015bisection} during this project.

>>>>

Tagging adds labels to objects.
Unlike how electrons and muons are very cleanly separated however, jet tagging
is a more noisy affair.

For jets in $\twoljets$, $b$-tagging is used to identify jets which are
more likely to have originated from $b$ quarks;
these tags serve to improve our separation of $t\bar t$ backgrounds
(since their weak decays almost always produce $b$ quarks), and
of signals producing $Z/h \rightarrow b\bar b$ decays in the GMSB model.

@@

\subsection{Overlap removal}

@@

To be precise, the stransverse mass explores how to split the observed
$\ptmiss$ between the two visible decay products in an event, and can be
defined as
\begin{equation}
\mttwo(a_\mu, b_\mu, m)
=
\min_{\vec p + \vec q=\ptmiss}
\max
\begin{Bmatrix}
m_T(a_\mu + \{\!\sqrt{m^2 - \vec p_T^{\:2}},\,\vec p\,\}_\mu)\\
m_T(b_\mu + \{\!\sqrt{m^2 - \vec q_T^{\:2}},\,\vec q\,\}_\mu)\\
\end{Bmatrix}
,
\end{equation}
in which $m_T^2(p_\mu) = p_0^2 - p_1^2 - p_2^2$~\cite{lester1999measuring}.
As an extension, one can assign different masses $m_p$ and $m_q$ to the
the two invisible products~\cite{lester2015bisection}.

Numerical evaluation of $\mttwo$ can be performed efficiently with interval
bisection algorithms, which seek the least resonance mass for which the
transverse masses allow any compatible assignment such that
$\vec p + \vec q = \ptmiss$.
Testing this compatibility reduces to testing for the intersection of two
ellipses, one for each transverse
mass~\cite{cheng2008minimal, lester2015bisection}.

Public code for calculating $\mttwo$ is available in a Python
library~\cite{gillam2021mt2}, to which I contributed a faster and more robust
implementation of the bisection algorithm by
Lester and Nachman~\cite{lester2015bisection} during this project.
